---
title: "Workout1-bailey-bounds.Rmd"
author: "Bailey Bounds"
date: "9/30/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading Packages
```{r}
library(readr)
library(dplyr)
library(ggplot2)
```

#Loading Data
```{r}
dat <- read_csv('../data/nba2018-teams.csv')
```

###Basic Rankings
```{r}
rank_team_by_salary <- arrange(
                          summarise(
                            group_by(dat, team),
                            total_salary = sum(salary)), 
                          desc(total_salary))

ggplot(data = rank_team_by_salary, aes(x = reorder(team, total_salary), y = total_salary)) + geom_bar(stat = 'identity', alpha = 0.5) + coord_flip() + labs(x = "Team", y = "Salary (in millions)", title = "NBA Teams ranked by Total Salary") + geom_hline(yintercept = mean(rank_team_by_salary$total_salary), color = "red", size = 2, alpha = 0.5)
ggsave(filename = "workout01-bailey-bounds_files/rank_team_by_salary.pdf", width = 7, height = 5)
```
```{r}
rank_team_by_points <- arrange(
                          summarise(
                            group_by(dat, team),
                            total_points = sum(points)), 
                          desc(total_points))

ggplot(data = rank_team_by_points, aes(x = reorder(team, total_points), y = total_points)) + geom_bar(stat = 'identity', alpha = 0.5) + coord_flip() + labs(x = "Team", y = "Points", title = "NBA Teams ranked by Total Points") + geom_hline(yintercept = mean(rank_team_by_points$total_points), color = "red", size = 2, alpha = 0.5)

ggsave(filename = "workout01-bailey-bounds_files/rank_team_by_points.pdf", width = 7, height = 5)
```

```{r}
rank_team_by_eff <- arrange(
                          summarise(
                            group_by(dat, team),
                            total_eff = sum(efficiency)), 
                          desc(total_eff))

ggplot(data = rank_team_by_eff, aes(x = reorder(team, total_eff), y = total_eff)) + geom_bar(stat = 'identity', alpha = 0.5) + coord_flip() + labs(x = "Team", y = "Efficiency", title = "NBA Teams ranked by Total Efficiency") + geom_hline(yintercept = mean(rank_team_by_eff$total_eff), color = "red", size = 2, alpha = 0.5)

ggsave(filename = "workout01-bailey-bounds_files/rank_team_by_eff.pdf", width = 7, height = 5)
```

###My own Ranking system
```{r}
dat <- mutate(dat, SPM = points/minutes)

rank_team_by_SPM <- arrange(
                          summarise(
                            group_by(dat, team),
                            total_SPM = sum(SPM)), 
                          desc(total_SPM))

ggplot(data = rank_team_by_SPM, aes(x = reorder(team, total_SPM), y = total_SPM)) + geom_bar(stat = 'identity', alpha = 0.5) + coord_flip() + labs(x = "Team", y = "Scores per Minute", title = "NBA Teams ranked by Scores per Minute") + geom_hline(yintercept = mean(rank_team_by_SPM$total_SPM), color = "red", size = 2, alpha = 0.5)

ggsave(filename = "workout01-bailey-bounds_files/rank_team_by_spm.pdf", width = 7, height = 5)
```

* I chose to rank teams by score per minute simply because in order to win you have to score the most points
 
#Comments and Reflections:
 
 * Yes this was my first time, and this file structure makes sense to me
 * Yes, and yes it is important since everyone's file structure on their computer is very different so controlling for that by just moving inside the project directory makes lots of sense
 * Yes, and I don't like rscript as much as rmarkdown, I like rmarkdown a lot, but I am becoming more familiar with it. I wish there was an easier way to write out long multiple line comments and titles
 * I think before lab06 a lot of the things that weren't discussed like the data dictionary or sink etc were pretty confusing
 * I thought the ggplot wasn't too difficult for the team rankings
 * No
 * 5 hours
 * R script for make-teams-table
 * figuring out sink and write_csv and using this file structure
 
